Results

### 2018-04-08 02_analysis.Rmd
Move survey details to additional analysis
Move full models out; compare all single conditions

## Attention check #2

```{r attention-check-2}
results %>% count(attention2_correct)
```

@@

```{r fig-amount-bars, fig.width=9, fig.height=2.75}
plot_amount_summary <- ggplot(results, aes(x = amount_donate)) +
  geom_histogram(bins = 20, fill = ngo_blue) +
  scale_x_continuous(labels = dollar) +
  labs(x = NULL, y = NULL) +
  theme_ngos(18) +
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank())

@@

# Interaction models with extra controls
m_amount_c_full <- update(m_amount_c, . ~ . + 
                            favor_humanitarian_bin + favor_human_rights_bin + favor_development_bin +
                            give_charity_3 + volunteer + political_knowledge_bin +
                            ideology_bin + education_bin + religiosity_bin +
                            income_bin + age_bin)

m_amount_ci_full <- update(m_amount_ci, . ~ . + 
                             favor_humanitarian_bin + favor_human_rights_bin + favor_development_bin +
                             give_charity_3 + volunteer + political_knowledge_bin +
                             ideology_bin + education_bin + religiosity_bin +
                             income_bin + age_bin)

m_amount_cif_full <-update(m_amount_cif, . ~ . + 
                             favor_humanitarian_bin + favor_human_rights_bin + favor_development_bin +
                             give_charity_3 + volunteer + political_knowledge_bin +
                             ideology_bin + education_bin + religiosity_bin +
                             income_bin + age_bin)
```

```{r tbl-models-amount, warning=FALSE, results="asis"}
huxreg(m_amount_c, m_amount_ci, m_amount_cif, 
       m_amount_c_full, m_amount_ci_full, m_amount_cif_full,
       coefs = clean_coefs_named,
       statistics = model_stats_bayes,
       stars = NULL) %T>% 
  print_hux() %>% 
  to_md(max_width = 100) %>% 
  cat(file = file.path(here(), "output", "tables", "tbl-models-amount.md"))
```

## Coefficient plot

```{r models-plot}
coefs_amount <- data_frame(model_name = c("Basic model", "Full model"),
                           model = list(m_amount_cif,
                                        m_amount_cif_full)) %>% 
  mutate(tidy = model %>% map(~ tidyMCMC(., conf.int = TRUE, conf.level = 0.9,
                                         conf.method = "HPDinterval"))) %>% 
  unnest(tidy) %>% 
  left_join(clean_coefs, by = "term") %>% 
  filter(term_clean != "Intercept")

ggplot(coefs_amount, aes(x = estimate, y = fct_rev(term_clean_fct), 
                         color = fct_rev(model_name))) +
  geom_pointrangeh(aes(xmin = conf.high, xmax = conf.low), 
                   position = position_dodgev(height = 0.5)) +
  geom_vline(xintercept = 0) + 
  scale_color_manual(values = c(ngo_red, ngo_blue), 
                     guide = guide_legend(title = NULL, reverse = TRUE)) +
  labs(x = "Posterior median estimate + 90% credible interval", y = NULL) +
  theme_ngos() +
  theme(panel.grid.major.y = element_blank())
```

@@

@@

@@

@@

@@

```{r tbl-all-amount-diffs, results="asis"}
bind_rows(diffs_coef_pairs_detail_c,
          diffs_coef_pairs_detail_ci,
          diffs_coef_pairs_detail_cif) %>% 
  select(Issue = issue, Funding = funding, 
         `No crackdown − crackdown (median)` = median, 
         `p(∆ > 0)` = p.greater0, `p(∆ < 0)` = p.less0, `p(∆ ≠ 0)` = p.diff.not0) %>% 
  pandoc.table.return(missing = "—", 
                      caption = 'Median difference between amounts donated in "no crackdown" (control) and "crackdown" conditions') %T>%
  cat() %>% 
  cat(file = file.path(here(), "output", "tables", "tbl-amount-diffs.md"))
```

@@

# Interaction models with extra controls
m_likely_c_full <- update(m_likely_c, . ~ . + 
                            favor_humanitarian_bin + favor_human_rights_bin + favor_development_bin +
                            give_charity_3 + volunteer + political_knowledge_bin +
                            ideology_bin + education_bin + religiosity_bin +
                            income_bin + age_bin)

m_likely_ci_full <- update(m_likely_ci, . ~ . + 
                             favor_humanitarian_bin + favor_human_rights_bin + favor_development_bin +
                             give_charity_3 + volunteer + political_knowledge_bin +
                             ideology_bin + education_bin + religiosity_bin +
                             income_bin + age_bin)

m_likely_cif_full <-update(m_likely_cif, . ~ . + 
                             favor_humanitarian_bin + favor_human_rights_bin + favor_development_bin +
                             give_charity_3 + volunteer + political_knowledge_bin +
                             ideology_bin + education_bin + religiosity_bin +
                             income_bin + age_bin)
```

```{r tbl-models-likely, warning=FALSE, results="asis"}
huxreg(m_likely_c, m_likely_ci, m_likely_cif, 
       m_likely_c_full, m_likely_ci_full, m_likely_cif_full,
       coefs = clean_coefs_named,
       statistics = model_stats_bayes,
       stars = NULL) %T>% 
  print_hux() %>% 
  to_md(max_width = 100) %>% 
  cat(file = file.path(here(), "output", "tables", "tbl-models-likelihood.md"))
```

## Coefficient plot

@@

@@

@@

@@

```{r tbl-all-likely-diffs, results="asis"}
bind_rows(diffs_coef_likely_pairs_detail_c,
          diffs_coef_likely_pairs_detail_ci,
          diffs_coef_likely_pairs_detail_cif) %>% 
  select(Issue = issue, Funding = funding, 
         `No crackdown − crackdown (median)` = median, 
         `p(∆ > 0)` = p.greater0, `p(∆ < 0)` = p.less0, `p(∆ ≠ 0)` = p.diff.not0) %>% 
  pandoc.table.return(missing = "—", 
                      caption = 'Median difference between likelihood to donate in "no crackdown" (control) and "crackdown" conditions') %T>%
  cat() %>% 
  cat(file = file.path(here(), "output", "tables", "tbl-likelihood-diffs.md"))
```

>>>>

@@

```{r fig-amount-bars, fig.width=9, fig.height=2.75}
plot_amount_summary <- ggplot(results, aes(x = amount_donate)) +
  geom_histogram(bins = 20, fill = ngo_blue) +
  scale_x_continuous(labels = dollar) +
  labs(x = NULL, y = NULL) +
  theme_ngos() +
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank())

@@

# Models with just issue and just funding
m_amount_i <- update(m_amount_c, . ~ issue)
m_amount_f <- update(m_amount_c, . ~ funding)
```

```{r tbl-models-amount, warning=FALSE, results="asis"}
# Get subset of coefficients
coefs_to_include <- list(m_amount_c, m_amount_ci, m_amount_cif) %>% 
  map(~ tidy(.)) %>% bind_rows() %>% distinct(term) %>% pull(term)

huxreg(m_amount_c, m_amount_ci, m_amount_cif, 
       coefs = clean_coefs_named[clean_coefs_named %in% coefs_to_include],
       statistics = model_stats_bayes,
       stars = NULL) %T>% 
  print_hux() %>% 
  to_md(max_width = 100) %>% 
  cat(file = file.path(here(), "output", "tables", "tbl-models-amount.md"))
```

@@

```{r amount-median-i}
newdata_conditions_i <- results %>% expand(nesting(issue))

chains_fitted_i <- posterior_linpred(m_amount_i, 
                                     newdata = newdata_conditions_i)

coef_summary_i <- newdata_conditions_i %>% 
  bind_cols(tidyMCMC(as.mcmc(chains_fitted_i), estimate.method = "median",
                     conf.int = TRUE, conf.level = 0.9, conf.method = "HPDinterval"))
```

```{r amount-median-f}
newdata_conditions_f <- results %>% expand(nesting(funding))

chains_fitted_f <- posterior_linpred(m_amount_f, 
                                     newdata = newdata_conditions_f)

coef_summary_f <- newdata_conditions_f %>% 
  bind_cols(tidyMCMC(as.mcmc(chains_fitted_f), estimate.method = "median",
                     conf.int = TRUE, conf.level = 0.9, conf.method = "HPDinterval"))
```

@@

```{r plot-single-amount-medians, warning=FALSE, fig.width=7, fig.height=2.5}
coef_summary_singles <- bind_rows(coef_summary_c, coef_summary_i, coef_summary_f) %>% 
  gather(condition, value, crackdown, issue, funding) %>% 
  filter(!is.na(value)) %>% 
  mutate(value = fct_inorder(value, ordered = TRUE),
         condition = fct_inorder(str_to_title(condition), ordered = TRUE))

plot_amount_singles <- ggplot(coef_summary_singles, aes(y = estimate, x = value)) + 
  geom_pointrange(aes(ymin = conf.low, ymax = conf.high, color = condition)) +
  scale_y_continuous(labels = dollar) +
  scale_color_manual(values = c(ngo_green, ngo_blue, ngo_red), guide = FALSE) +
  labs(x = NULL, y = "Median amount donated") +
  theme_ngos() +
  theme(panel.grid.major.x = element_blank(),
        strip.text = element_text(margin = margin(5, 0, 2, 0, "pt"))) +
  facet_wrap(~ condition, scales = "free_x")

plot_amount_singles %T>%
  print() %T>%
  ggsave(., filename = file.path(here(), "output", "figures", "amount_single_summary.pdf"),
         width = 7, height = 2.5, units = "in", device = cairo_pdf) %>% 
  ggsave(., filename = file.path(here(), "output", "figures", "amount_single_summary.png"),
         width = 7, height = 2.5, units = "in", type = "cairo", dpi = 300)
```

@@

```{r amount-diffs-i}
diffs_coef_pairs_i <- chains_fitted_i %>% 
  as_data_frame() %>% 
  magrittr::set_colnames(levels(newdata_conditions_i$issue)) %>% 
  mcmc_pairwise_diffs()

diffs_coef_pairs_detail_i <- tidy_diffs(diffs_coef_pairs_i)

pairs_plot_data_i <- diffs_coef_pairs_i %>%
  gather(pair, value) %>%
  mutate(pair1 = pair) %>%
  separate(pair1, into = c("group1", "group2"), sep = " − ") %>%
  mutate(pair = ifelse(nchar(pair) > 25,
                       str_replace(pair, "−", "−\n"),
                       pair))
```

```{r amount-diffs-f}
diffs_coef_pairs_f <- chains_fitted_f %>% 
  as_data_frame() %>% 
  magrittr::set_colnames(levels(newdata_conditions_f$funding)) %>% 
  mcmc_pairwise_diffs()

diffs_coef_pairs_detail_f <- tidy_diffs(diffs_coef_pairs_f)

pairs_plot_data_f <- diffs_coef_pairs_f %>%
  gather(pair, value) %>%
  mutate(pair1 = pair) %>%
  separate(pair1, into = c("group1", "group2"), sep = " − ") %>%
  mutate(pair = ifelse(nchar(pair) > 25,
                       str_replace(pair, "−", "−\n"),
                       pair))
```

@@

**Compare only individual conditions:**

```{r plot-single-amount-diffs, fig.width=7, fig.height=2.5}
diffs_plot_data_singles <- bind_rows(pairs_plot_data_c,
                                     pairs_plot_data_i,
                                     pairs_plot_data_f) %>% 
  mutate(pair = fct_inorder(pair, ordered = TRUE))

diffs_coef_pairs_detail_singles <- bind_rows(diffs_coef_pairs_detail_c,
                                             diffs_coef_pairs_detail_i,
                                             diffs_coef_pairs_detail_f) %>%
  mutate(pair = ifelse(nchar(pair) > 25,
                       str_replace(pair, "−", "−\n"),
                       pair),
         pair = fct_inorder(pair, ordered = TRUE))

plot_diffs_singles <- ggplot() +
  geom_density(data = diffs_plot_data_singles, 
               aes(x = value, fill = pair),
               colour = NA, alpha = 0.4) +
  geom_segment(data = diffs_coef_pairs_detail_singles, 
               aes(x = q5, xend = q95, y = 0, yend = 0, group = pair),
               size = 3) +
  geom_vline(data = diffs_coef_pairs_detail_singles, 
             aes(xintercept = median), size = 0.25) +
  geom_vline(xintercept = 0, linetype = "dotted") +
  scale_x_continuous(labels = dollar) +
  scale_fill_manual(values = c(ngo_green, ngo_blue, ngo_red), guide = FALSE) +
  labs(x = "Difference in medians") +
  theme_ngos(density = TRUE) +
  facet_wrap(~ pair)

plot_diffs_singles %T>%
  print() %T>% 
  ggsave(., filename = file.path(here(), "output", "figures", "amount-singles-diffs.pdf"),
         width = 7, height = 2.5, units = "in", device = cairo_pdf) %>% 
  ggsave(., filename = file.path(here(), "output", "figures", "amount-singles-diffs.png"),
         width = 7, height = 2.5, units = "in", type = "cairo", dpi = 300)
```

```{r tbl-single-amount-diffs, results="asis"}
bind_rows(diffs_coef_pairs_detail_c,
          diffs_coef_pairs_detail_i,
          diffs_coef_pairs_detail_f) %>% 
  select(`Frame` = pair, `∆~median~` = median, 
         `p(∆ > 0)` = p.greater0, `p(∆ < 0)` = p.less0, `p(∆ ≠ 0)` = p.diff.not0) %>% 
  pandoc.table.return(missing = "—", 
                      caption = "Median difference between likelihood to donate across single conditions") %T>%
  cat() %>% 
  cat(file = file.path(here(), "output", "tables", "tbl-amount-single-diffs.md"))
```

**Compare nested conditions (what we're really most concerned about):**

@@

```{r tbl-all-amount-diffs, results="asis"}
bind_rows(diffs_coef_pairs_detail_c,
          diffs_coef_pairs_detail_ci,
          diffs_coef_pairs_detail_cif) %>% 
  select(Issue = issue, Funding = funding, 
         `No crackdown − crackdown~median~` = median, 
         `p(∆ > 0)` = p.greater0, `p(∆ < 0)` = p.less0, `p(∆ ≠ 0)` = p.diff.not0) %>% 
  pandoc.table.return(missing = "—", 
                      caption = 'Median difference between amounts donated in "no crackdown" (control) and "crackdown" conditions') %T>%
  cat() %>% 
  cat(file = file.path(here(), "output", "tables", "tbl-amount-diffs.md"))
```

@@

# Models with just issue and just funding
m_likely_i <- update(m_likely_c, . ~ issue)
m_likely_f <- update(m_likely_c, . ~ funding)
```

```{r tbl-models-likely, warning=FALSE, results="asis"}
# Get subset of coefficients
coefs_to_include <- list(m_likely_c, m_likely_ci, m_likely_cif) %>% 
  map(~ tidy(.)) %>% bind_rows() %>% distinct(term) %>% pull(term)

huxreg(m_likely_c, m_likely_ci, m_likely_cif, 
       coefs = clean_coefs_named[clean_coefs_named %in% coefs_to_include],
       statistics = model_stats_bayes,
       stars = NULL) %T>% 
  print_hux() %>% 
  to_md(max_width = 100) %>% 
  cat(file = file.path(here(), "output", "tables", "tbl-models-likelihood.md"))
```

@@

```{r likely-median-i}
newdata_conditions_i <- results %>% expand(nesting(issue))

chains_fitted_likely_i <- posterior_linpred(m_likely_i, 
                                            newdata = newdata_conditions_i, 
                                            transform = TRUE)

coef_summary_likely_i <- newdata_conditions_i %>% 
  bind_cols(tidyMCMC(as.mcmc(chains_fitted_likely_i), estimate.method = "median",
                     conf.int = TRUE, conf.level = 0.9, conf.method = "HPDinterval"))

plot_likely_i <- ggplot(coef_summary_likely_i, aes(y = estimate, x = issue)) + 
  geom_pointrange(aes(ymin = conf.low, ymax = conf.high), color = ngo_green) + 
  scale_y_continuous(labels = percent) +
  labs(x = NULL, y = "Probability of donating") +
  theme_ngos() +
  theme(panel.grid.major.x = element_blank())
```

```{r likely-median-f}
newdata_conditions_f <- results %>% expand(nesting(funding))

chains_fitted_likely_f <- posterior_linpred(m_likely_f, 
                                            newdata = newdata_conditions_f, 
                                            transform = TRUE)

coef_summary_likely_f <- newdata_conditions_f %>% 
  bind_cols(tidyMCMC(as.mcmc(chains_fitted_likely_f), estimate.method = "median",
                     conf.int = TRUE, conf.level = 0.9, conf.method = "HPDinterval"))

plot_likely_f <- ggplot(coef_summary_likely_f, aes(y = estimate, x = funding)) + 
  geom_pointrange(aes(ymin = conf.low, ymax = conf.high), color = ngo_green) + 
  scale_y_continuous(labels = percent) +
  labs(x = NULL, y = "Probability of donating") +
  theme_ngos() +
  theme(panel.grid.major.x = element_blank())
```

@@

```{r likely-diffs-i}
diffs_coef_likely_pairs_i <- chains_fitted_likely_i %>% 
  as_data_frame() %>% 
  magrittr::set_colnames(levels(newdata_conditions_i$issue)) %>% 
  mcmc_pairwise_diffs()

diffs_coef_likely_pairs_detail_i <- tidy_diffs(diffs_coef_likely_pairs_i)

pairs_likely_plot_data_i <- diffs_coef_likely_pairs_i %>%
  gather(pair, value) %>%
  mutate(pair1 = pair) %>%
  separate(pair1, into = c("group1", "group2"), sep = " − ") %>%
  mutate(pair = ifelse(nchar(pair) > 25,
                       str_replace(pair, "−", "−\n"),
                       pair))
```

```{r likely-diffs-f}
diffs_coef_likely_pairs_f <- chains_fitted_likely_f %>% 
  as_data_frame() %>% 
  magrittr::set_colnames(levels(newdata_conditions_f$funding)) %>% 
  mcmc_pairwise_diffs()

diffs_coef_likely_pairs_detail_f <- tidy_diffs(diffs_coef_likely_pairs_f)

pairs_likely_plot_data_f <- diffs_coef_likely_pairs_f %>%
  gather(pair, value) %>%
  mutate(pair1 = pair) %>%
  separate(pair1, into = c("group1", "group2"), sep = " − ") %>%
  mutate(pair = ifelse(nchar(pair) > 25,
                       str_replace(pair, "−", "−\n"),
                       pair))
```

@@

**Compare only individual conditions:**

```{r plot-single-likely-diffs, fig.width=7, fig.height=2.5}
diffs_likely_plot_data_singles <- bind_rows(pairs_likely_plot_data_c,
                                            pairs_likely_plot_data_i,
                                            pairs_likely_plot_data_f) %>% 
  mutate(pair = fct_inorder(pair, ordered = TRUE))

diffs_coef_likely_pairs_detail_singles <- bind_rows(diffs_coef_likely_pairs_detail_c,
                                                    diffs_coef_likely_pairs_detail_i,
                                                    diffs_coef_likely_pairs_detail_f) %>%
  mutate(pair = ifelse(nchar(pair) > 25,
                       str_replace(pair, "−", "−\n"),
                       pair),
         pair = fct_inorder(pair, ordered = TRUE))

plot_diffs_likely_singles <- ggplot() +
  geom_density(data = diffs_likely_plot_data_singles, 
               aes(x = value, fill = pair),
               colour = NA, alpha = 0.4) +
  geom_segment(data = diffs_coef_likely_pairs_detail_singles, 
               aes(x = q5, xend = q95, y = 0, yend = 0, group = pair),
               size = 3) +
  geom_vline(data = diffs_coef_likely_pairs_detail_singles, 
             aes(xintercept = median), size = 0.25) +
  geom_vline(xintercept = 0, linetype = "dotted") +
  scale_x_continuous(labels = percent) +
  scale_fill_manual(values = c(ngo_green, ngo_blue, ngo_red), guide = FALSE) +
  labs(x = "Difference in medians") +
  theme_ngos(density = TRUE) +
  facet_wrap(~ pair)

plot_diffs_likely_singles %T>%
  print() %T>% 
  ggsave(., filename = file.path(here(), "output", "figures", "likelihood-singles-diffs.pdf"),
         width = 7, height = 2.5, units = "in", device = cairo_pdf) %>% 
  ggsave(., filename = file.path(here(), "output", "figures", "likelihood-singles-diffs.png"),
         width = 7, height = 2.5, units = "in", type = "cairo", dpi = 300)
```

```{r tbl-single-likely-diffs, results="asis"}
bind_rows(diffs_coef_likely_pairs_detail_c,
          diffs_coef_likely_pairs_detail_i,
          diffs_coef_likely_pairs_detail_f) %>% 
  select(`Frame` = pair, `∆~median~` = median, 
         `p(∆ > 0)` = p.greater0, `p(∆ < 0)` = p.less0, `p(∆ ≠ 0)` = p.diff.not0) %>% 
  pandoc.table.return(missing = "—", 
                      caption = "Median difference between likelihood to donate across single conditions") %T>%
  cat() %>% 
  cat(file = file.path(here(), "output", "tables", "tbl-likelihood-single-diffs.md"))
```

**Compare nested conditions (what we're really most concerned about):**

@@

```{r tbl-all-likely-diffs, results="asis"}
bind_rows(diffs_coef_likely_pairs_detail_c,
          diffs_coef_likely_pairs_detail_ci,
          diffs_coef_likely_pairs_detail_cif) %>% 
  select(Issue = issue, Funding = funding, 
         `No crackdown − crackdown~median~` = median, 
         `p(∆ > 0)` = p.greater0, `p(∆ < 0)` = p.less0, `p(∆ ≠ 0)` = p.diff.not0) %>% 
  pandoc.table.return(missing = "—", 
                      caption = 'Median difference between likelihood to donate in "no crackdown" (control) and "crackdown" conditions') %T>%
  cat() %>% 
  cat(file = file.path(here(), "output", "tables", "tbl-likelihood-diffs.md"))
```
